%-------------------------
% Resume in Latex
% Author : Mayank Sharma 
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{fontawesome}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.3in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{3pt}
	\scshape\raggedright\large
}
{}{0pt}{}[\color{gray}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\ExternalLink}{%
	\tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{% 
		\begin{scope}[x=1ex, y=1ex]
			\clip (-0.1,-0.1) 
			--++ (-0, 1.2) 
			--++ (0.6, 0) 
			--++ (0, -0.6) 
			--++ (0.6, 0) 
			--++ (0, -1);
			\path[draw, 
			line width = 0.5, 
			rounded corners=0.5] 
			(0,0) rectangle (1,1);
		\end{scope}
		\path[draw, line width = 0.5] (0.5, 0.5) 
		-- (1, 1);
		\path[draw, line width = 0.5] (0.6, 1) 
		-- (1, 1) -- (1, 0.6);
	}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\href{https://msharma.in/}{\huge Mayank Sharma}} & 
	H-315/5, IIT Kanpur \vspace{2pt} \\
	Third Year Undergraduate &
	+91-9461240034  $\vert$ 
	\href{mailto:mayank8019@gmail.com}{mayank8019@gmail.com}\\
	Computer Science \& Engineering &
	\faGithub\hspace{0.3em}\href{https://github.com/mayanksha}{mayanksha} $\vert$
	\faLinkedin \hspace{0.3em}\href{https://www.linkedin.com/in/mayanksha}{mayanksha} $\vert$
	\faHome \hspace{0.3em}\href{https://msharma.in}{msharma.in}
	\\
\end{tabular*}
\vspace{-8pt}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Indian Institute of Technology, Kanpur}{Kanpur, India}
{B.Tech in Computer Science \& Engineering; CGPA 6.25/10.0}{July 2016 -- present}\vspace{0pt}
\resumeSubheading
{Children Senior Secondary School, Dadabari, Kota (Raj.)}{Kota, Rajasthan}
{AISSCE Class XII; \textbf{92.0\%}}{2016}\vspace{0pt}
\resumeSubheading
{Central Academy Sr. Sec. School}{Chittorgarh, Rajasthan}
{CBSE Class X; \textbf{CGPA 10.0/10.0}}{2014}
\resumeSubHeadingListEnd
\vspace{-8pt}

%-----------KEY SCHOLASTIC ACHIEVEMENTS-----------------
\section{Key Scholastic Achievements}
%\begin{itemize}[noitemsep]
\begin{itemize}
	\setlength\itemsep{0pt}
	\item \textbf{All India Rank 630} in JEE Advanced 2016 among 200 thousand selected candidates.
	\item \textbf{All India Rank 2237} in JEE Main 2016 among 1.2 million candidates.
	\item \textbf{All India Rank 854}, KVPY Fellowship Award (2015) awarded by Department of Science and Technology, India.
	\item Awarded \textbf{Certificate of Merit} for being in \textbf{State Top 1-Percent} in Nation Standard Examination in Physics (NSEP) in 2016.\vspace*{-8pt}
\end{itemize}


%-----------EXPERIENCE-----------------
\section{Internship Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Software Developer Intern, EarlySalary}{Pune, India}
{Pickup System Case Allocation Automation (Mentor: Vivek Jain)}{May 2018 - July 2018}
\vspace{2pt}
%\begin{itemize}[noitemsep]
\begin{itemize}
	\item[$\circ$] Worked on the backend of a scalable web app, and helped migration from existing PHP based system.
	\item[$\circ$] Implemented centralized Authentication \& Authorization using \textbf{Jumpcloud’s Directory-as-a-Service}.
	\item[$\circ$] Helped design APIs and Algorithms, to retrieve a new case and automatically assign to a Pickup Agency based upon its priority in a cluster, as soon as a new case is added.
	\item[$\circ$] Developed Microservices for Lambda based REST APIs and deloyed them on Lambda using Claudia.js.
	\item[$\circ$] \textbf{Techonologies Used}: Express.js with Node.js, Typescript, Redis (as session store), MySQL, LDAP, AWS Services.\vspace*{-8pt}
\end{itemize}
\resumeSubHeadingListEnd


%-----------SELF PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubheading
		{Zero Shot Sketch Based Image Retrieval (SBIR)}{Kanpur, India}
{Intro. to Machine Learning (Prof. Piyush Rai)}{Aug. 2018 - Nov. 2018}
\vspace{2pt}
\begin{itemize}
	\item[$\circ$] Implemented Principal Component Analysis \& tried extending it to zero-shot setting, to test how it \\ generalizes to other unseen classes.
	\item[$\circ$] Used TU Berlin Sketch Dataset and learned how to extract features to be later compared to hand-drawn sketches. 
	\item[$\circ$] Used canny edge detection to convert images to basic sketches in OpenCV. 
	\item[$\circ$] Modeled these images using caffe and tensorflow by taking hints and code snippets from various research papers.
\end{itemize}
\resumeSubheading
{Linux From Scratch}{ \textbf{\hfill}\href{https://github.com/mayanksha/lfs} {\faGithub \hspace{0.1em} GitHub (/mayanksha/lfs)}}
{ACA Semester Project}{Jan. 2017 - Apr. 2017}
\vspace{2pt}
	\begin{itemize}
				\item Developed a {\bf Student Search} in bash which scraped data from Office Automation Portal. 
				\item Used the ZeromQ library in python to implement client server model to play Collatz Conjecture Game.
				\item Created a \textbf{SysVInit} based bare-bones linux distribution, compiling packages from tarballs, building upon the host system kernel and finally compiling the kernel for new distro.
	\end{itemize}
\resumeSubHeadingListEnd

%-----------Skills-----------------
\section{Technical Skills}
\begin{itemize}[noitemsep]
	\item
		\textbf{Programming : }
		Javascript and Typescript (\textit{Proficient}), Golang (\textit{Fluent}), C++, C, Bash Scripting
	\item
		\textbf{Web : }
		Express.js with Node.js \textit{(Fluent)}, Angular 4, MongoDB (Mongoose), Nginx \& Openresty 

	\item
		\textbf{Databases \& Utilities : }
		MySQL, Redis, LDAP, Git, \LaTeX, Vim, AutoCAD
	\item
		\textbf{Operating Systems : }
		Linux (Arch, Ubuntu \& LFS), Windows
		\vspace*{-5pt}
\end{itemize}
\vspace*{-8pt}

%-----------POR-----------------
\section{Positions of Responsibility}

\begin{itemize}
	\setlength\itemsep{0pt}
\item \textbf{Head, Web Development, Entrepreneurship Cell, IIT Kanpur}	
	\hfill \textit{(April ‘18 - present)}
	\begin{itemize}
		\setlength\itemsep{0pt}
		\item Spearheading a team of 10+ Senior Web Developer Executives,	
			effectively distributing development work and collaborating in a Git Organization.
		\item Developed Campus Ambassador and Events Registration Portals. (MEAN Stack)
	\end{itemize}

\item \textbf{Webmaster, Hall 5, IIT Kanpur}
	\hfill \textit{(Nov. ‘17 - Oct. ‘18)}
	\begin{itemize}
		\setlength\itemsep{0pt}
		\item Redesigned and revamped the webpage of Hall 5, IIT Kanpur.\vspace*{-8pt}
	\end{itemize}

\end{itemize}\vspace*{-6pt}

%-----------Relevant Courses-----------------
\section{Relevant Courses}
{\fontsize{10pt}{1em}\upshape\color{black}
	\begin{tabular*}{\textwidth}{l l l}
		Systems \& Cyber Security ($i$) 
		& \hspace{3em} Blockchain Technology \& Applications ($i$) 
		& \hspace{3em} Database Systems ($i$)
		\\
		Operating Systems
		& \hspace{3em} Intro. to Machine Learning
		& \hspace{3em} Software Engineering ($i$)
		\\
		Data Structures \& Algorithms 
		&\hspace{3em} Discrete Mathematics 
		&\hspace{3em} Introduction to Programming
		%&\hspace{6em} Algorithms 2 ($i$)
		%&\hspace{6em} Theory Of Computation
		\\
		 %&\hspace{6em} 
			%&\hspace{6em} 
		%Logic in Computer Science  \vspace{0pt}
	\end{tabular*}
}
\hspace*{\fill} 
$i$: In progress\\

\vspace{-0.6cm}

%-----------Extracurriculars-----------------
\section{Extracurriculars \& Hobbies}
\begin{itemize}
	\setlength\itemsep{0pt}
	\item \fontsize{10pt}{1em} Won the Inter-hall Capture-the-Flag (CTF) competition participating from the pool Mughals.
	\item	A fitness enthusiast, who likes to lead an active lifestyle, regularly hitting the gym and lost 20 Kgs weight in the first year. 
	\item Part of School Basketball Team playing at District Level, winning accolades for the team.
\end{itemize}

%-----------Interests-----------------
\section{Interests}
\begin{itemize}
	\setlength\itemsep{0pt}
	\item Cyber-Security and Reverse Engineering. Working with low-level C/C++ Code and finding exploits in them. 
	\item Architecture and Scalability aspects of various highly performant Backend Systems.	
	\item Open-source development. Currently, working towards bugs in Gnome-Maps application for the Gnome Organization. IRC (irc.gnome.org - mayanksha)
\end{itemize}
%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
