\cvsection{Work Experience}
\begin{cventries}

  \cventry
  {Improve Google Drive support in GNOME Virtual File System (GVfs), Mentor: Ondřej Holý}
  {Google Summer of Code, GNOME Organization}
  {India}
  {Summer 2019}
  {
    \begin{cvitems}
    \item Ported libgdata from (\textit{autotools + make}) to (\textit{meson + ninja}) build system, writing build files to compile and link a shared library consisting of  100+ object files, thereby \textbf{improving build times by $\sim$40\%}.
    \item Developed a new API (\texttt{GDataDocumentsProperty}) for libgdata (C library for Google Drive API) from scratch to support Properties Resource on File objects.
    \item Augmented copy, move, delete and make\_directory operations in GVfs (earlier disabled) with \texttt{GDataDocumentsProperty} API, by creating a volatile path to the new entry, thereby handling differences between a \textbf{POSIX-based fs} \textit{vs} a \textbf{database-backed fs} (Google Drive).
    \item Developed a \textbf{regression test-suite} from scratch for the Google backend in GVfs. The test-suite is planned to be a part of \textbf{Gitlab based CI system} and uses GIO operations on a dummy google account to test the backend.
    \item All the code is open-sourced on GNOME's Gitlab and is planned to make way into \textbf{GNOME's 3.36 stable release}.
    \end{cvitems}
  }

  \cventry
  {Microservice Orchestration Layer (\textit{Mozart}), Mentor: Kshirodra Meher}
  {Software Engineer Intern, WalmartLabs}
  {Bengaluru, India}
  {Summer 2019}
  {
    \begin{cvitems}
    \item Worked on the Service Orchestration Layer (REST based) for Walmart International, to create a \textbf{one-stop solution for 162 Microservices}.
    \item Helped migration from a monolithic Oracle ATG (Java based) system to a \textbf{Bulk-Head Design Pattern based architecture} in node.js.
    \item Developed \textbf{"mozart-utils"}, an npm package published to Walmart's in-grown npm repository providing standardized utility functions to over 8 sub-modules in a mono-repo.
    \item Collaborated with team to develop \textbf{20 endpoints}, with all 20 being used in production systems for Walmart Mexico.
    \item Contributed to seen improvements in performance \textbf{from less than 15,000 to $\sim$ 90,000 concurrent users/hr} on a single instance.
    \item Received a direct Pre-Placement-Offer (PPO) on showing outstanding performance amongst 120 interns.
    % \item Employed CI/CD best practices to develop and deploy on Walmart’s ingrown CI (Looper, based on Jenkins) and CD (Concord) systems.
    \end{cvitems}
  }

  \cventry
  {Pickup System Case Allocation Automation, Mentor: Vivek Jain}
  {Software Developer Intern, EarlySalary}
  {Pune, India}
  {Summer 2018}
  {
    \begin{cvitems}
	\item Worked on the backend of a scalable web app, and helped migration from an existing PHP based system to the one based on node.js.
	\item Implemented centralized Authentication and Authorization, using JumpCloud’s Directory-as-a-Service \textbf{(LDAP)}.
\item Helped \textbf{design APIs and Algorithms}, to retrieve and automatically assign a new case to a Pickup Agency based upon its priority in a cluster.
\item Developed \textbf{Microservices for Lambda based REST APIs}, and Prevented XSS into the existing MySQL Databases.
% \item Helped deploy the REST API as AWS Lambda Functions using Claudia.js.
\item Techonologies Used: Express.Js with Node.Js, Typescript, MySQL,
LDAP, AWS Lambda Services
    \end{cvitems}
  }

\end{cventries}
